### 2021-05-11 concurrency/docs/theory/theory.tex
fix typos

\newcommand{\ltIntersect}{\sqcup}
\newcommand{\ltLe}{\sqsubseteq}
\newcommand{\ltGe}{\sqsupseteq}
\DeclareMathOperator{\lifetime}{lifetime}
\DeclareMathOperator{\borrowed}{borrowed}

@@

An SSM is given by \textbf{(i)} some PCM state $S, \cdot$, \textbf{(ii)} an invariant $inv : S \to \bool$ and a sharded transition $\rightsquigarrow : S \times S$. For a sharded state
machine, the invariant inductivity predicate is given by,
\[
  inv(a \cdot c) \land (a \rightsquigarrow b) \implies inv(b \cdot c)
\]
(Note: $\rightsquigarrow$ is neither transitive nor required to be monotonic here. However, an alternative definition would require $\rightsquigarrow$ to be monotonic, in which case we could
simplify the inductivity predicate to $inv(a) \land (a \rightsquigarrow b) \implies inv(b)$.)

>>>>

\newcommand{\ltIntersect}{\sqcap}
\newcommand{\ltLe}{\sqsubseteq}
\newcommand{\ltGe}{\sqsupseteq}
\DeclareMathOperator{\lifetime}{lifetime}
\DeclareMathOperator{\borrowed}{borrowed}

@@

An SSM is given by \textbf{(i)} some PCM state $S, \cdot$, \textbf{(ii)} an invariant $inv : S \to \bool$ and a sharded transition $\rightsquigarrow : S \times S \to \bool$. For a sharded state
machine, the invariant inductivity predicate is given by,
\[
  inv(a \cdot c) \land (a \rightsquigarrow b) \implies inv(b \cdot c)
\]
(Note: $\rightsquigarrow$ is neither transitive nor required to be monotonic here. However, an alternative definition would require $\rightsquigarrow$ to be monotonic, in which case we could
simplify the inductivity predicate to $inv(a) \land (a \rightsquigarrow b) \implies inv(b)$.)
